Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
form

The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
synthesis of stabilizing controllers for continuous plants described as
transfer functions, by exploiting bit-accurate verification of
software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While this work
also makes use of a CEGIS-based technique, the approach is restricted to
synthesizing digital controllers for stable closed-loop systems described
via transfer function models.  By contrast, in the current paper we consider
a state-space representation of the physical system, which is known to present
various advantages over transfer function representation \cite{Astrom08}:
(i)~easy to generalize for the multivariate systems (i.e., with multiple inputs 
and outputs); (ii)~shows the state-to-input relationships offering an internal 
model of the system; and (iii)~allows to synthesize control systems with
guarantees about the internal dynamics, e.g., to synthesize controllers that make
the closed-loop system \emph{safe}. This work focuses on the \emph{safety} of 
internal states, such property is usually overlooked in the previous cited 
works, but plays an important role in real world systems, where system
variables cannot assume arbitrary real values. Moreover, our work integrates an
abstraction/refinement step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} synthesizes
correct-by-design embedded control software, in a Matlab toolbox.  It is based on the abstraction
of a physical system to an equivalent finite-state machine and on the
computation of reachability properties over the finite-state machine.  Based
on this safety specification, Pessoa can synthesize
embedded controller software for a range of properties.
The embedded controller software can be more complicated than
the state-feedback control we synthesized, and the properties 
available cover more detail.
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the quantization error
introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
synthesizing fixed-point digital controllers.

>>>>

The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
synthesis of stabilizing controllers for continuous plants described as
transfer functions, by exploiting bit-accurate verification of
software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While
this work also makes use of a CEGIS-based technique, the approach is
restricted to synthesizing digital controllers for stable closed-loop
systems described via transfer function models.  By contrast, in the current
paper we consider a state-space representation of the physical system, which
is known to present various advantages over transfer function
representation~\cite{Astrom08}: (i)~easy to generalize for the multivariate
systems (i.e., with multiple inputs and outputs); (ii)~shows the
state-to-input relationships offering an internal model of the system; and
(iii)~allows to synthesize control systems with guarantees about the
internal dynamics, e.g., to synthesize controllers that make the closed-loop
system \emph{safe}.  This work focuses on the \emph{safety} of internal
states, such property is usually overlooked in the previous cited works, but
plays an important role in real world systems, where system variables cannot
assume arbitrary real values.  Moreover, our work integrates an
abstraction/refinement step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
control software, in a Matlab toolbox.  It is based on the abstraction of a
physical system to an equivalent finite-state machine and on the computation
of reachability properties over the finite-state machine.  Based on this
safety specification, Pessoa can synthesize embedded controller software for
a range of properties.  The embedded controller software can be more
complicated than the state-feedback control we synthesized, and the
properties available cover more detail.
%
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the quantization error
introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
synthesizing fixed-point digital controllers.
